PAR Digital: Tecnologia em Prol do Ensino Inclusivo

### 2024-07-02 Paper.tex
name defined

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Insert Your Title Here}
\subtitle{Subtitle (optional)}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
%\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\author{G.K.M. Tobin}
%\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as a
  paper formatted for publication in the proceedings of the WebMedia. Based on the ``acmart'' document class, this
  paper presents and explains the formatting elements an author may use to prepare his paper.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

@@

\section{Introduction}

If you are new to publishing with WebMedia, this document is a valuable
guide to preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the paper template.

The ``\verb|webmedia|'' document class must be used to prepare papers
for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|webmedia|'' document class must
be used to prepare your
double-blind initial submission of the paper.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|webmedia|'' document class is
the {\itshape template style} which corresponds to the kind of publication. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[sigconf]{webmedia}
\end{verbatim}

WebMedia adopts the sigconf template style.

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, you must use the {\itshape template parameter} \verb|anonymous,review| for the ``double-blind'' submission. For ``double-blind'' submission, please use the following string as the first command in the
source file:
\verb|\documentclass[sigconf,anonymous,review]{webmedia}|.

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

@@

\section{Typefaces}

@@

\section{Title Information}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{PAR Digital: Tecnologia em Prol do Ensino Inclusivo}

% \subtitle{Subtitle (optional)}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Daniele Cássia}
\affiliation{%
  \institution{Departamento de Ciência de Computação}
  \institution{Universidade Federal de Minas Gerais}
  \city{Belo Horizonte}
  \country{Brasil}}
\email{danielecassia@ufmg.br}

\vspace{1cm}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.

\begin{abstract}
  Este artigo apresenta uma descrição dos objetivos e funcionalidades do
  PAR Digital, demonstrando como o software pode transformar a prática
  educacional inclusiva.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{software, tecnologia, educação, plano educacional individualizado, inclusão}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
% \begin{teaserfigure}
%   \includegraphics[width=\textwidth]{sampleteaser}
%   \caption{Seattle Mariners at Spring Training, 2010.}
%   \Description{Enjoying the baseball game from the third-base
%   seats. Ichiro Suzuki preparing to bat.}
%   \label{fig:teaser}
% \end{teaserfigure}

@@

\section{Introdução}

O PAR Digital é uma ferramenta tecnológica desenvolvida com base em anos de estudo
e pesquisa pela Faculdade de Educação da Universidade Federal de Minas Gerais, PAR
significa Planejar, Aplicar, Rever, ações necessárias para que o ensino seja eficaz
para os alunos com deficiência.

\section{Objetivo}
O objetivo do PAR Digital é proporcionar uma ferramenta acessível e intuitiva 
que facilite o preenchimento e a gestão do Plano Educacional Individualizado (PEI), 
essencial para o desenvolvimento educacional dos alunos com deficiência. Desenvolvido
 a partir de princípios do Desenho Universal de Aprendizagem (DUA) e de uma parceria 
 com o Atendimento Educacional Especializado (AEE), o sistema visa integrar-se de 
 maneira eficiente na rotina diária dos educadores, promovendo um ensino inclusivo 
 e personalizado.
% \url{https://www.acm.org/publications/proceedings-template}.

\section{Arquitetura}

A estrutura do projeto é organizada de maneira a facilitar a manutenção e a expansão 
do mesmo.

As principais tecnologias utilizadas no projeto incluem React.js, uma biblioteca 
JavaScript para construção de interfaces de usuário, escolhida por sua eficiência 
na criação de componentes reutilizáveis e desempenho otimizado. O TypeScript é 
usado para adicionar tipagem estática ao código JavaScript, aumentando a robustez 
e facilitando a manutenção. O Redux é empregado para o gerenciamento de estado da 
aplicação, ideal para aplicações de médio e grande porte que necessitam de um 
controle mais sofisticado do estado. A biblioteca Material-UI é utilizada para 
implementar o design system do Google Material Design, enquanto o Axios serve 
como cliente HTTP para realizar requisições a APIs. Ferramentas como Jest e 
React Testing Library são utilizadas para testes automatizados, garantindo a 
qualidade e a funcionalidade do código.

O fluxo de dados na aplicação é gerenciado pelo Redux, que centraliza o estado da 
aplicação em um único store. As ações são despachadas a partir dos componentes, 
que são tratadas pelos `reducers` para atualizar o estado global. Essa abordagem 
facilita a depuração e o desenvolvimento de novas funcionalidades, uma vez que o 
estado da aplicação se torna previsível e controlado.

A estilização da aplicação é feita utilizando CSS-in-JS com a biblioteca Material-UI,
 permitindo uma aplicação consistente do design system através dos componentes. 
 A utilização de temas facilita a customização e a manutenção do estilo visual da 
 aplicação.

Para a integração e entrega contínua (CI/CD), o projeto utiliza ferramentas como 
o GitHub Actions, configurado para executar testes automatizados e builds a cada 
commit, garantindo que a aplicação se mantenha estável e pronta para deployment. 
O deploy é realizado em um servidor localizado na UFMG, permitindo uma escalabilidade
 fácil e eficiente.

@@

\section{Funcionalidades}

@@

\section{Licença}

\section{Perspectivas}
